\documentclass[review]{elsarticle}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}

\journal{Target journal to be confirmed}

\begin{document}

\begin{frontmatter}

\title{Parameter-Efficient Adaptation of Geospatial Foundation Models for Flood Inundation Mapping under Spatial Distribution Shift}

\author[aff1]{Author Name}
\affiliation[aff1]{organization={Affiliation to be confirmed}}

\begin{abstract}
Geospatial foundation models have shown promise for Earth observation tasks, but
their practical value for data-scarce disaster mapping remains sensitive to
geographic distribution shift, compute cost, and evaluation design. This study
will benchmark parameter-efficient adaptation strategies for flood inundation
mapping using the public Sen1Floods11 dataset. We compare conventional
segmentation baselines with geospatial foundation model adaptation under
cross-event and low-label settings, reporting segmentation accuracy,
trainable-parameter counts, compute cost, and spatial failure modes. Results
will clarify when resource-aware foundation-model adaptation improves flood
mapping and when simpler baselines remain competitive.
\end{abstract}

\begin{keyword}
GeoAI \sep geospatial foundation model \sep flood mapping \sep remote sensing \sep parameter-efficient fine-tuning \sep responsible AI
\end{keyword}

\end{frontmatter}

\section{Introduction}

Draft after the first completed baseline experiments. The introduction should
motivate rapid flood mapping, spatial transfer, and compute-aware GeoAI without
overclaiming.

\section{Related Work}

Cover Sen1Floods11 \cite{bonafilia2020sen1floods11}, geospatial foundation
models \cite{jakubik2023foundation}, recent surveys
\cite{huang2025survey}, TerraTorch \cite{marsocci2025terratorch}, and
responsible GeoAI \cite{li2026responsible}.

\section{Data}

Describe dataset version, GCS source, labels, bands, invalid masks, splits, and
event metadata.

\section{Methods}

Describe baselines, foundation-model adaptation, PEFT variants, training
protocol, and implementation details.

\section{Experimental Design}

Describe in-distribution, cross-event, cross-region, and low-label settings.
Define metrics before reporting results.

\section{Results}

Only insert metrics generated by committed configs and logs.

\section{Discussion}

Discuss practical value, failure modes, compute tradeoffs, and limitations.

\section{Conclusion}

Summarize evidence-backed findings.

\bibliographystyle{elsarticle-num}
\bibliography{../references/paper}

\end{document}

